workshop

### 2023-02-14 scripts/workshop/workshop.Rmd
incidence and prevalence plots

>>>>

```{r}
incidence <- data %>% group_by(WetAltID, Month.1) %>% summarize(incidence = sum(RV.Status))

incidence %>% ggplot(.,aes(x=Month.1, y=incidence)) + geom_col() + facet_grid(vars(WetAltID))
```

```{r}
comm_data <- readRDS(here("processed_data","comm_data.rds"))
comm_data %>% ggplot(.,aes(x=Month.1, y=Prevalence)) + geom_point() + facet_wrap(~WetAltID, nrow = 5, ncol = 4)
```
